## Version history

- *30 March:* Recoding part 2, polishing
- *13 March:* adding definitions,  recoding revision part 1
- *5 March 2026:* Initial version

## Objectives

This document presents a descriptive analysis  of the time use of parents of children up to age 16 comparing men and women:

  - The time use activities should include working, parenting, caring, housework, sleep, social etc. 
  - These could be broken down by highest qualification, social class, occupation, age banded, number of children etc.
  - In the first instance using 2014-15 UK TUS.

## Analysis

There are a number of key notions to keep in mind when looking at time use data:

1. The unit of observation is the day  of a respondent. Each respondent may have one or two days worth of data - typically one weekday, one day at the weekend. Unless otherwise specified, results below are averaged across both days.

2. There are two main approaches to  estimating activity duration according to the denominator used: 

-  Restricting the denominator to activity participants only. Estimates derived that way  provide realistic values of  duration for those who engage in the activity, but it has the disadvantage of relying on subsamples that may differ in composition, thus complicating direct comparisons.

-  Alternatively, one can  use  the full sample of relevant observations as the denominator, including respondents who reported no time in the activity. This approach enhances the robustness of comparisons between groups, but produces lower average duration estimates due to the inclusion of zero-minute observations.




```{r open_datasets}
library(dplyr)
library(haven)
library(reshape2)
library(ggplot2)
library(spatstat)
library(parallel)
library(survey)
library(srvyr)
library(RColorBrewer)
cbplt<-c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
datadir<-"~/Data/tus/UKDA-8128-stata/stata/stata11_se/"
pl<-read_dta(paste0(datadir,"uktus15_individual.dta")) %>%   filter(DVAge>=16  & IndOut==11)%>%select(serial,pnum,DMSex,DM016,DVAge,dhiqual,dsoc,dnssec8)
el<-read_dta(paste0(datadir,"uktus15_diary_ep_long.dta"))%>% filter(DVAge>=16 & IndOut==11) 
ew<-read_dta(paste0(datadir,"uktus15_diary_wide.dta"))%>% filter(DVAge>=16 & IndOut==11)%>%select(serial,pnum,daynum,DiaryDay_Act,dmonth,
                      act1_1:act1_144,dia_wt_a,dia_wt_b)

```

```{r labels}  
### Plain English version of the categories of activity we are going to use for the tempograms

lab.l<-c("Sleep","Self-care","Work and education","Housework/shopping",
         "Caring","Volunteering/helping", "Leisure", "Physical activity","Travel")
var.l<-c("slp","scr","wrk","rwk","car","vol","lei","phy","tra")
```


```{r recode_long}
el$wkd<-ifelse(el$DiaryDay_Act==1 | el$DiaryDay_Act==7,"Weekend","Weekday")

el<-el|> mutate(
  slp.t =ifelse((whatdoing>0 & whatdoing<210) | eptime==5310 ,eptime,0),
  scr.t =ifelse(whatdoing==0 | (whatdoing>=210  & whatdoing<1000),eptime,0),
  wrk.t=ifelse((whatdoing>=1000 & whatdoing<2210) | whatdoing == 9110,eptime,0),
  rwk.t=ifelse((whatdoing>=3000 & whatdoing<3800 ),eptime,0),
  car.t=ifelse((whatdoing>=3800 & whatdoing<4000) ,eptime,0),
  vol.t=ifelse((whatdoing>=4000 & whatdoing<5000) ,eptime,0),
  lei.t=ifelse((whatdoing>=5000 & whatdoing<5310) | 
                 (whatdoing>=6200 & whatdoing<9000)  | whatdoing==2210, eptime,0),
    phy.t=ifelse(whatdoing>=6000  & whatdoing<6200,eptime,0),
  tra.t=ifelse(whatdoing>=9000 & whatdoing<9940 &  whatdoing != 9110 ,eptime,0)
)

for(i in 1:length(var.l)){
el<-el|>group_by(serial,pnum,daynum)|>mutate(tmp=sum(eval(parse(text=paste0(var.l[i],".t")))))  
names(el)[which(names(el)=="tmp")]<-paste0(var.l[i],".d")
}
```


```{r recode_pers}

### Number of children
pl$nrkid<-ifelse(pl$DM016>2,"3+",as.character(pl$DM016))
pl$nrkid<-factor(pl$nrkid,labels=c("None", "One", "Two","Three or more"))

### Sex * whther parent
pl$chsx<-as_factor(paste((pl$DM016>0),as_factor(pl$DMSex)))
pl$chsx<-factor(pl$chsx,levels=levels(pl$chsx)[c(1,4,3,2)],labels = c("F, kids","M, kids","F, no kids","M, no kids"))

### age bands
pl<-pl|> mutate(
            ageb=case_when(
                  DVAge<16 ~ "<16",
                  DVAge>=16 & DVAge<26 ~ "16-25",
                  DVAge>=26 & DVAge<36 ~ "26-35",
                  DVAge>=36 & DVAge<46 ~ "36-45",
                  DVAge>=46 & DVAge<56 ~ "46-55",
                  DVAge>=56 & DVAge<=99 ~ "55+"
            ),
            ageb=as.factor(ageb)
            
)
                  
```


```{r merge}
#We can now merge the episode dataset with the person-level one into a day-level one

pts<-merge(el|>filter(epnum==1),pl,by=c("serial","pnum"),all=F)


options(survey.lonely.psu = 'adjust')
options(survey.multicore = T)

```


## Univariate descriptive statistics: mean, median and coefficient of variation.


```{r desc}
  pts.s<-pts|>  #filter(eval(parse(text=paste0(i,">0  & wkd==\"Weekday\"")))) |>
                as_survey_design(id=psu,strata =strata,weights = dia_wt_a)


res.sex<-data.frame()
res.sex.p<-data.frame()
res.wkd<-data.frame()
res.nrkid<-data.frame()
res.age<-data.frame()
res.hiq<-data.frame()
res.nss<-data.frame()
res.soc<-data.frame()

for(i in paste0(var.l,".d")){
  pts.sp<-pts|>  filter(eval(parse(text=paste0(i,">0")))) |>
                as_survey_design(id=psu,strata =strata,weights = dia_wt_a)

### Overall

  t1<-svyby(~eval(parse(text=i)), ~chsx, pts.s, svymean,vartype = "ci")
  t2<-svyby(~eval(parse(text=i)), ~chsx, pts.s, svyquantile,vartype = "ci",quantile=0.5)
  t3<-(svyby(~eval(parse(text=i)), ~chsx, pts.s, svyvar,vartype = "ci"))
tmp.s<-cbind(t1,t2[,2:4],sqrt(t3[,c(2:4)])/t1[,c(2:4)])

### Overall, participants

  t1<-svyby(~eval(parse(text=i)), ~chsx, pts.sp, svymean,vartype = "ci")
  t2<-svyby(~eval(parse(text=i)), ~chsx, pts.sp, svyquantile,vartype = "ci",quantile=0.5)
  t3<-(svyby(~eval(parse(text=i)), ~chsx, pts.sp, svyvar,vartype = "ci"))
tmp.sp<-cbind(t1,t2[,2:4],sqrt(t3[,c(2:4)])/t1[,c(2:4)])


### Weekdays vs weekends

  t1<-svyby(~eval(parse(text=i)), ~chsx+wkd, pts.s, svymean,vartype = "ci")
#  t2<-svyby(~eval(parse(text=i)), ~chsx+wkd, pts.s, svyquantile,vartype = "ci",quantile=0.5)
  t3<-(svyby(~eval(parse(text=i)), ~chsx+wkd, pts.s, svyvar,vartype = "ci"))
tmp.w<-cbind(t1,sqrt(t3[,c(3:5)])/t1[,c(3:5)])


### Number of kids
  t1<-svyby(~eval(parse(text=i)), ~chsx+nrkid, pts.s, svymean,vartype = "ci")
  t3<-(svyby(~eval(parse(text=i)), ~chsx+nrkid, pts.s, svyvar,vartype = "ci"))
tmp.n<-cbind(t1,sqrt(t3[,c(3:5)])/t1[,c(3:5)])

### Age bands
  t1<-svyby(~eval(parse(text=i)), ~chsx+ageb, pts.s, svymean,vartype = "ci")
  t3<-(svyby(~eval(parse(text=i)), ~chsx+ageb, pts.s, svyvar,vartype = "ci"))
tmp.a<-cbind(t1,sqrt(t3[,c(3:5)])/t1[,c(3:5)])

### Qualifications
  t1<-svyby(~eval(parse(text=i)), ~chsx+as_factor(dhiqual), pts.s, svymean,vartype = "ci")
  t3<-(svyby(~eval(parse(text=i)), ~chsx+as_factor(dhiqual), pts.s, svyvar,vartype = "ci"))
tmp.h<-cbind(t1,sqrt(t3[,c(3:5)])/t1[,c(3:5)])

### Occupations
  t1<-svyby(~eval(parse(text=i)), ~chsx+as_factor(dsoc), pts.s, svymean,vartype = "ci")
  t3<-(svyby(~eval(parse(text=i)), ~chsx+as_factor(dsoc), pts.s, svyvar,vartype = "ci"))
tmp.o<-cbind(t1,sqrt(t3[,c(3:5)])/t1[,c(3:5)])

### Social class
  t1<-svyby(~eval(parse(text=i)), ~chsx+as_factor(dnssec8), pts.s, svymean,vartype = "ci")
  t3<-(svyby(~eval(parse(text=i)), ~chsx+as_factor(dnssec8), pts.s, svyvar,vartype = "ci"))
tmp.c<-cbind(t1,sqrt(t3[,c(3:5)])/t1[,c(3:5)])


res.sex<-rbind(res.sex,tmp.s)
res.sex.p<-rbind(res.sex.p,tmp.sp)
res.wkd<-rbind(res.wkd,tmp.w)

res.nrkid<-rbind(res.nrkid,tmp.n)
res.age<-rbind(res.age,tmp.a)
res.hiq<-rbind(res.hiq,tmp.h)
res.nss<-rbind(res.nss,tmp.c)
res.soc<-rbind(res.soc,tmp.o)

}

```




### Gender (all respondents)
::: {.panel-tabset}

#### **Estimates**

```{r sex_all_tab}

res.sex<-cbind(Activity=rep(lab.l,each=4),res.sex)
names(res.sex)[2:ncol(res.sex)]<-c("Group", "Mean","Mean_Low","Mean_Up","Median","Med_Low","Med_Up","CV","CV_Low","CV_Up")
kableExtra::kable(res.sex|>
                    filter(Group=="F, kids" | Group=="M, kids")|>
                    select(Activity,Group,Mean,Mean_Low,Mean_Up,CV),digits = c(0,0,0,0,0,2),row.names = F)

```

#### **Plot**

```{r sex_all_plot}
ggplot(res.sex|>filter(Group=="F, kids" | Group=="M, kids")|>
                select(Activity,Group,Mean,Mean_Low,Mean_Up), 
       aes(x = Mean, y = interaction(Group, Activity, sep = " - "))) +
  geom_errorbarh(aes(xmin = Mean_Low, xmax = Mean_Up), 
                 height = 0.2) +
  geom_point(size = 2) +
  labs(x = "Daily time (minutes)", y = "Groups and activities", title = "Time spent on activities by gender and parenting status") +
  theme_minimal()
```

::: 


### Gender (participants)

::: {.panel-tabset}

#### **Estimates**
```{r sex_part_tab}

res.sex.p<-cbind(Activity=rep(lab.l,each=4),res.sex.p)
names(res.sex.p)[2:ncol(res.sex.p)]<-c("Group", "Mean","Mean_Low","Mean_Up","Median","Med_Low","Med_Up","CV","CV_Low","CV_Up")
kableExtra::kable(res.sex.p|>
                    filter(Group=="F, kids" | Group=="M, kids")|>
                    select(Activity,Group,Mean,Mean_Low,Mean_Up),digits = 0,row.names = F)

```

#### **Plot**

```{r sex_part_plot}

ggplot(res.sex.p|>filter(Group=="F, kids" | Group=="M, kids")|>
                select(Activity,Group,Mean,Mean_Low,Mean_Up), 
       aes(x = Mean, y = interaction(Group, Activity, sep = " - "))) +
  geom_errorbarh(aes(xmin = Mean_Low, xmax = Mean_Up), 
                 height = 0.2) +
  geom_point(size = 2) +
  labs(x = "Daily time (minutes)", y = "Groups and activities",
       title = "Time spent on activities by gender and parenting status") +
  theme_minimal()
```

:::

### Weekend vs weekdays 

::: {.panel-tabset}

#### **Estimates**

```{r sex_wkd_tab}

res.wkd<-cbind(Activity=rep(lab.l,each=8),res.wkd)
names(res.wkd)[2:ncol(res.nrkid)]<-c( "Group", "Diary","Mean","Mean_Low","Mean_Up","CV","CV_Low","CV_Up")
kableExtra::kable(res.wkd|>
                    filter(Group=="F, kids" | Group=="M, kids")|>
                    select(Activity,Diary,Group,Mean,Mean_Low,Mean_Up),digits = 0,row.names = F)

```

#### **Plot**

```{r sex_wkd_plot}

ggplot(res.wkd|>filter(Group=="F, kids" | Group=="M, kids") |>
                select(Activity,Diary,Group,Mean,Mean_Low,Mean_Up), 
       aes(x = Mean, y = paste(Group, Diary,sep = " - "))) +
    facet_wrap(~Activity,scale="free_x") +
  geom_errorbarh(aes(xmin = Mean_Low, xmax = Mean_Up), 
                 height = 0.2) +
  geom_point(size = 2) +
  labs(x = "Daily time (minutes)", y = "Day type and sex",
       title = "Time spent on activities by gender and parenting status") +
  theme_minimal()
```

:::

### Number of children

::: {.panel-tabset}

#### **Estimates**

```{r sex_nrkid_tab}

res.nrkid<-cbind(Activity=rep(lab.l,each=8),res.nrkid)
names(res.nrkid)[2:ncol(res.nrkid)]<-c("Gender", "Children", "Mean","Mean_Low","Mean_Up","CV","CV_Low","CV_Up")
kableExtra::kable(res.nrkid|>
                    filter((Gender=="F, kids" | Gender=="M, kids") & Children!="None")|>
                    select(Activity,Children,Gender,Mean,Mean_Low,Mean_Up),
                  digits = 0,row.names = F)

```


#### **Plot**

```{r sex_nrkid_plot}

ggplot(res.nrkid|> filter((Gender=="F, kids" | Gender=="M, kids") & Children!="None")|>
                    select(Activity,Children,Gender,Mean,Mean_Low,Mean_Up), aes(x = Mean, y = interaction(Gender, Children, sep = " - "))) +
  facet_wrap(~Activity) +
  geom_errorbarh(aes(xmin = Mean_Low, xmax = Mean_Up), 
                 height = 0.2) +
  geom_point(size = 2) +
  labs(x = "Daily time (minutes)", y = "Number of children and sex",
       title = "Time spent on activities by gender and family size") +
  theme_minimal()

```

:::

### Age banded

::: {.panel-tabset}

#### **Estimates**

```{r sex_age_tab}

res.age<-cbind(Activity=rep(lab.l,each=20),res.age)
names(res.age)[2:ncol(res.age)]<-c( "Gender","Age", "Mean","Mean_Low","Mean_Up","CV","CV_Low","CV_Up")
kableExtra::kable(res.age|>
                    filter(Gender!="F, no kids" & Gender!="M, no kids" )|>
                    select(Activity,Age,Gender,Mean,Mean_Low,Mean_Up),
                  digits = 2,row.names = F)

```

#### **Plot**
```{r sex_age_plot}

ggplot(res.age|>filter(Gender!="F, no kids" & Gender!="M, no kids" ) |>
         select(Activity,Gender,Age,Mean,Mean_Low,Mean_Up), aes(x = Mean, y = interaction(Gender, Activity, sep = " - "))) +
  facet_wrap(~ Age,ncol=2) +
  geom_errorbarh(aes(xmin = Mean_Low, xmax = Mean_Up), 
                 height = 0.2) +
  geom_point(size = 2) +
  labs(x = "Daily time (minutes)", y = "Groups and activities",
       title = "Time spent on activities by gender and age)") +
  theme_minimal()
```
:::

### Highest qualification
::: {.panel-tabset}

#### **Estimates**

```{r sex_qul_tab}

res.hiq<-cbind(Activity=rep(lab.l,each=26),res.hiq)
names(res.hiq)[2:ncol(res.age)]<-c( "Gender","Qualification", "Mean","Mean_Low","Mean_Up","CV","CV_Low","CV_Up")
kableExtra::kable(res.hiq|>
                    filter(Gender!="F, no kids" & Gender!="M, no kids" & Qualification != "Don't know")|>
                    select(Activity,Qualification,Gender,Mean,Mean_Low,Mean_Up),
                  digits=0,row.names = F)

```

#### **Plot**

```{r sex_qul_plot}

ggplot(res.hiq|>filter(Gender!="F, no kids" & Gender!="M, no kids"  & Qualification != "Don't know")  |>
         select(Activity,Gender,Qualification,Mean,Mean_Low,Mean_Up), 
aes(x = Mean, y = interaction(Gender, Activity, sep = " - "))) +
  facet_wrap(~ Qualification) +
  geom_errorbarh(aes(xmin = Mean_Low, xmax = Mean_Up), 
                 height = 0.2) +
  geom_point(size = 2) +
  labs(x = "Daily time (minutes)", y = "Age bands and sex",
        title = "Time spent on activities by gender and age") +
  theme_minimal()
```
:::

### Occupation
::: {.panel-tabset}

#### **Estimates**

```{r sex_occ_tab}

```{r sex_occ}
res.soc<-cbind(Activity=rep(lab.l,each=41),res.soc)
names(res.soc)[2:ncol(res.soc)]<-c("Gender","Occupation", "Mean","Mean_Low","Mean_Up","CV","CV_Low","CV_Up")
kableExtra::kable(res.soc|>
                    filter(Gender!="F, no kids" & Gender!="M, no kids" & Occupation != "Item not applicable")|>
                    select(Activity,Occupation,Gender,Mean,Mean_Low,Mean_Up),
                  digits=0,row.names = F)

```

#### **Plot**
```{r sex_occ_plot}

ggplot(res.soc|>filter(Gender!="F, no kids" & Gender!="M, no kids"  & Occupation != "Item not applicable") |>
         select(Activity,Gender,Occupation,Mean,Mean_Low,Mean_Up), aes(x = Mean, y = interaction(Gender, Activity, sep = " - "))) +
  facet_wrap(~ Occupation) +
  geom_errorbarh(aes(xmin = Mean_Low, xmax = Mean_Up), 
                 height = 0.2) +
  geom_point(size = 2) +
  labs(x = "Daily time (minutes)", y = "Activities and sex",
       title = "Time spent on activities by gender and occupation)") +
  theme_minimal()
```
:::

### Social class

::: {.panel-tabset}

#### **Estimates**

```{r sex_cla_tab}

res.nss<-cbind(Activity=rep(lab.l,each=40),res.nss)
names(res.nss)[2:ncol(res.nss)]<-c("Gender", "Class", "Mean","Mean_Low","Mean_Up","CV","CV_Low","CV_Up")
kableExtra::kable(res.nss|>
                    filter(Gender!="F, no kids" & Gender!="M, no kids" & Class != "Item not applicable"  & Class != "No answer/refused")|>
                    select(Activity,Class,Gender,Mean,Mean_Low,Mean_Up),digits=0,row.names = F)

```

#### **Plot**

```{r sex_cla_plot}

ggplot(res.nss|>filter(Gender!="F, no kids" & Gender!="M, no kids"  & Class != "Item not applicable" & Class != "No answer/refused") |>
         select(Activity,Gender,Class,Mean,Mean_Low,Mean_Up), aes(x = Mean, y = interaction(Gender, Activity, sep = " - "))) +
  facet_wrap(~ Class) +
  geom_errorbarh(aes(xmin = Mean_Low, xmax = Mean_Up), 
                 height = 0.2) +
  geom_point(size = 2) +
  labs(x = "Daily time (minutes)", y = "Sex and activities",
       title = "Time spent on activities by gender and NS-SEC social class)") +
  theme_minimal()


``` 

:::


## Appendix

### Definition of activities (HETUS nomenclature)

::: {.panel-tabset}

#### Sleep: 

  - Sleep
  - In bed not asleep
  - Sick in bed

#### Self-care: 
  - Unspecified personal care
  - Eating  
  - Unspecified other personal care
  - Wash and dress
  - Other specified personal care
  
#### Paid work and full-time education: 

  - Travel in the course of work
  - Unspecified employment,Unspecified main job
  - Working time in main job
  - Coffee and other breaks in main job
  - Working time in second job
  - Coffee and other breaks in second job
  - Unspecified activities related to employment
  - Lunch break
  - Other specified activities related to employment
  - Activities related to job seeking
  - Other specified activities related to employment
  - Unspecified study school or university
  - Unspecified activities related to school or university
  - Classes and lectures
  - Homework
  - other specified activities related to school or university

#### Housework, DIY and shopping:

  - Unspecified household and family care
  - Unspecified food management
  - Food preparation and baking
  - Dish washing
  - Preserving
  - Other specified food management
  - Unspecified household upkeep
  - Cleaning dwelling
  - Cleaning yard
  - Heating and water
  - Arranging household goods and materials
  - Disposal of waste
  - Other or unspecified household upkeep
  - Unspecified making and care for textiles
  - Laundry
  - Ironing
  - Handicraft and producing textiles
  - Other specified making and care for textiles
  - Gardening
  - Tending domestic animals
  - Caring for pets
  - Walking the dog
  - Other specified gardening and pet care
  - Unspecified construction and repairs
  - House construction and renovation
  - Repairs of dwelling
  - Making repairing and maintaining equipment
  - Woodcraft metalcraft sculpture and pottery
  - Other specified making repairing and maintaining equipment
  - Vehicle maintenance
  - Other specified construction and repairs
  - Unspecified shopping and services
  - Shopping mainly for food
  - Shopping mainly for clothing
  - Shopping mainly related to accommodation
  - Shopping or browsing at car boot sales or antique fairs
  - Window shopping or other shopping as leisure
  - Other specified shopping
  - Commercial and administrative services
  - Personal services
  - Other specified shopping and services
  - Household management not using the internet
  - Shopping for and ordering clothing via the internet
  - Unspecified household management using the internet
  - Shopping for and ordering unspecified goods and services via the internet
  - Shopping for and ordering food via the internet
  - Shopping for and ordering goods and services related to accommodation via theinternet
  - Shopping for and ordering mass media via the internet
  - Shopping for and ordering entertainment via the internet
  - Banking and bill paying via the internet
  - Other specified household management using the internet
  - Unspecified shopping
  - Shopping mainly for food
  - Shopping mainly for clothing
  - Shopping mainly related to accommodation
  - Shopping or browsing at car boot sales or antique fairs
  - Window shopping or other shopping as leisure
  - Other specified shopping
  - Commercial and administrative services
  - Personal services
  - Other specified shopping and services
  - Household management not using the internet
  - Shopping for and ordering clothing via the internet
  - Unspecified household management using the internet
  - Shopping for and ordering unspecified goods and services via the internet
  - Shopping for and ordering food via the internet
  - Shopping for and ordering goods and services related to accommodation via the internet
  - Shopping for and ordering mass media via the internet
  - Shopping for and ordering entertainment via the internet
  - Banking and bill paying via the internet
  - Other specified household management using the internet
  
#### Caring for children or adults

  - Unspecified childcare
  - Unspecified physical care & supervision of a child
  - Feeding the child
  - Other and unspecified physical care & supervision of a child
  - Teaching the child
  - Reading playing and talking with child
  - Accompanying child
  - Other or unspecified childcare

#### Helping / volunteering

  - Unspecified help to a non-dependent e.g. injured adult household member
  - Physical care of a non-dependent e.g. injured adult household member
  - Accompanying a non-dependent adult household member e.g. to hospital
  - Other specified help to a non-dependent adult household member
  - Unspecified help to a dependent adult household member
  - Physical care of a dependent adult household member e.g. Alzheimic parent
  - Accompanying a dependent adult household member e.g. Alzheimic
  - Other specified help to a dependent adult household member
  - Unspecified volunteer work and meetings
  - Unspecified participatory activities
  - Meetings
  - Religious activities
  - Other specified participatory activities
  - Unspecified organisational work
  - Work for an organisation
  - Volunteer work through an organisation
  - Other specified organisational work
  - Unspecified informal help to other households
  - Food management as help to other households
  - Household upkeep as help to other households
  - Gardening and pet care as help to other households
  - Construction and repairs as help to other households
  - Shopping and services as help to other households
  - Help to other households in employment and farming
  - Unspecified childcare as help to other households
  - Physical care and supervision of child as help to other household
  - Teaching non-coresident child
  - Reading playing & talking to non-coresident child
  - Accompanying non-coresident child
  - Physical care and supervision of own child as help to other household
  - Reading playing & talking to own non-coresident child
  - Accompanying own non-coresident child
  - Other specified childcare as help to other household
  - Unspecified help to an adult of another household
  - Physical care and supervision of an adult as help to another household
  - Accompanying an adult as help to another household
  - Other specified help to an adult member of another household
  - Other specified informal help to another household
  - Other specified informal help
  

####  Leisure

  - Unspecified productive exercise
  - Hunting and fishing
  - Picking berries mushroom and herbs
  - Other specified productive exercise
  - Unspecified sports related activities
  - Activities related to sports
  - Activities related to productive exercise
  - Unspecified social life and entertainment
  - Unspecified social life
  - Socialising with family
  - Visiting and receiving visitors
  - Celebrations
  - Telephone conversation
  - Other specified social life
  - Unspecified entertainment and culture
  - Cinema
  - Unspecified theatre or concerts
  - Plays musicals or pantomimes
  - Opera operetta or light opera
  - Concerts or other performances of classical music
  - Live music other than classical concerts, opera, and musicals
  - Dance performances
  - Other specified theatre or concerts
  - Art exhibitions and museums
  - Unspecified library
  - Borrowing books records audiotapes videotapes CDs VDs etc. from a library
  - Reference to books and other library materials within a library
  - Using internet in the library
  - Using computers in the library other than internet use
  - Reading newspapers in a library
  - Other specified library activities
  - Sports events
  - Other specified entertainment and culture
  - Visiting a historical site
  - Visiting a wildlife site
  - Visiting a botanical site
  - Visiting a leisure park
  - Visiting an urban park playground designated pl
  - Unspecified hobbies games and computing
  - Unspecified arts
  - Unspecified visual arts
  - Painting drawing or other graphic arts
  - Making videos taking photographs or related photographic activities
  - Other specified visual arts
  - Unspecified performing arts
  - Singing or other musical activities
  - Other specified performing arts
  - Literary arts
  - Other specified arts
  - Unspecified hobbies
  - Collecting
  - Correspondence
  - Other specified or unspecified arts and hobbies
  - Computing - programming
  - Unspecified information by computing
  - Information searching on the internet
  - Other specified information by computing
  - Unspecified communication by computer
  - Communication on the internet
  - Other specified communication by computing
  - Unspecified other computing
  - Skype or other video call
  - Other specified computing
  - Unspecified games
  - Solo games and play
  - Unspecified games and play with others
  - Billiards pool snooker or petanque
  - Chess and bridge
  - Other specified parlour games and play
  - Computer games
  - Gambling
  - Other specified games
  - Unspecified mass media
  - Unspecified reading
  - Reading periodicals
  - Reading books
  - Other specified reading
  - Unspecified TV video or DVD watching
  - Watching a film on TV
  - Watching sport on TV
  - Other specified TV watching
  - Unspecified video watching
  - Watching a film on video
  - Watching sport on video
  - Other specified video watching
  - Unspecified listening to radio and music
  - Unspecified radio listening
  - Listening to music on the radio
  - Listening to sport on the radio
  - Other specified radio listening
  - Listening to recordings

####  Physical activity

  - Unspecified sports and outdoor activities
  - Unspecified physical exercise
  - Walking and hiking
  - Taking a walk or hike that lasts at least miles or 1 hour
  - Other walk or hike
  - Jogging and running
  - Biking skiing and skating
  - Unspecified ball games
  - Indoor pairs or doubles games
  - Indoor team games
  - Outdoor pairs or doubles games
  - Outdoor team games
  - Other specified ball games
  - Gymnastics
  - Fitness
  - Unspecified water sports
  - Swimming
  - Other specified water sports
  - Other specified physical exercise


####  Travel

  - Travel to/from work
  - Travel to work from home and back only
  - Travel to work from a place other than home
  - Travel related to education
  - Travel escorting to/ from education
  - Travel related to household care
  - Travel related to shopping
  - Travel related to services
  - Travel escorting a child other than education
  - Travel escorting an adult other than education
  - Travel related to organisational work
  - Travel related to voluntary work and meetings
  - Travel related to informal help to other households
  - Travel related to religious activities
  - Travel related to participatory activities other than religious activities
  - Travel to visit friends/relatives in their homes not respondents household
  - Travel related to other social activities
  - Travel related to entertainment and culture
  - Travel related to other leisure
  - Travel related to physical exercise
  - Travel related to hunting & fishing
  - Travel related to productive exercise other than hunting & fishing
  - Travel related to gambling
  - Travel related to hobbies other than gambling
  - Travel related to changing locality
  - Travel to holiday base
  - Travel for day trip/just walk
  - Other specified travel

:::
  
